Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-03 response-to-reviewers.tex

\section{Referee 1}

\subsection{Main comments:}

\begin{enumerate}
\item The paper aims to contribute to an already large
  literature. The recent literature in this field focus on the
  identification of causal effects by using instrumental variable
  approaches (see, e.g., Isphording et al., 2014; Yao and van Ours,
  2015). However, I like the fact that the authors a very clear that
  they are not able to identify causal effects. This is, of course, a
  shortcoming and is limiting the overall contribution of the
  paper. Given the specific focus of International Journal of Manpower
  and the interests of its readership, I find that the paper is
  nevertheless providing a small, but still interesting
  contribution. By analysing data from Estonia and providing results
  on natives’ language skills the paper distinguished itself form
  large parts of the literature and adds some new results to our
  knowledge on the labour market effects of language skills.

  \begin{response}
    No response needed here.
  \end{response}
\item 
  \debug{OT: should refer to Toomet (2011), maybe there are more
    papers.  The effect is mainly coming from Tallinn and somewhat
    from education too, either do a table that disentangles these, or
    a plot (violin plot?) by group.}
  \debug{SKB: I did the estimation separated by regions, but not 
  separated by regions and educational level. We could add the regional
  breakdown in the appendix or add it as another extension to chapter 6.}
  My main concern is with some of their wage results. I find it
  puzzling that they don’t find a wage premium for Russian men who
  have Estonian language skills as they do find a sizeable significant
  effect of about 11 to 17 percent for Russian women and a significant
  positive effect for Estonians who speak Russian. Furthermore, they
  find that Estonian language skills do reduce the probability of
  being unemployed for Russians. Why is there a reduction in the
  probability of being unemployed, but no wage effect? Can we trust
  this result? Looking at the descriptive statistics (see Table 1) the
  wage for Russian men who speak Estonian seems to be higher compared
  to Russian men without the ability to speak Estonian (489.96 vs
  401.59). The authors should either provide more statistics on this
  result (if possible) or a more detailed discussion on potential
  reasons that lead to this finding.
\item
  \debug{OT: I'll do a rewrite after changes are made, hope it's
    sufficient.} 
  The paper needs to be checked for spelling and grammar
  errors. There are a number of typos and errors, which should be
  corrected in a revision. This would normally be a minor comment, but
  here the authors should take this comment very serious as there are
  so many mistakes.
\end{enumerate}

@@

\subsection{Minor comments:}

\begin{enumerate}
\item- The description of the estimation models in Chapter 4 should
  be more detailed. Please describe more specifically what exactly you
  are estimating. In particular the description of the second model
  estimating the time trend is very short.
  \debug{SKB: Svetlana modified the equations a bit. I added another table,
  which summarises the models.}
\item - The tables and figures should have notes that explain in more
  detail what is shown in the respective table and figure. For
  instance, the table notes should contain the included control
  variables, the sample period and the age restriction applied.
\item 
- Page 4: You write that you are only analysing individuals who are
working or actively looking for a job, but in line 35 on the same page
you write that inactivity is one of the included labour market
outcomes. Please clarify this and be clear in your description of what
is included in your sample.
\item 
  \debug{ot: let's make it equal (i.e. remove all observations with
    any of the variables missing.  Add a footnote that when we
    included all the variables, we still got the same results.}
  The sample size for different specification of the same analysis
should be the equal. Otherwise it is difficult to conclude whether the
changes in the coefficients are coming from the addition of more
controls or form the change in the size of the estimation sample.
\item 
- In the paper, you are only showing the results of the variables of
interest. I suggest to provide tables including all coefficients (not
the year dummies) in the Appendix. It might be interesting to see how
the coefficients of the control variables change across the different
models.
\item 
- All tables: Be consistent in the description of your tables. The
table notes and the labels for e.g., "observations", are inconsistent
across the different tables. 
\item
  \debug{ot: this was because of both 'B. Chiswick' and
    'B. R. Chiswick' in the bibtex file, and bibtex wanted to
    distinguish between these two guys.}
 Page 1: To cite Chiswick you are using different versions
(B. Chiswick and B. R. Chiswick).

### 2018-07-03 response-to-reviewers.tex

% -*- mode: LaTeX; mode: flyspell; -*-
% mode: Tex-Pdf -*-
\documentclass{article}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[bookmarks=TRUE,
            colorlinks,
            pdfpagemode=none,
            pdfstartview=FitH,
            citecolor=black,
            filecolor=black,
            linkcolor=blue,
            urlcolor=black,
            ]{hyperref}
\usepackage{graphicx}
\usepackage{icomma}
\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{setspace}
\usepackage[dvipsnames]{xcolor}
\usepackage{xspace}
\usepackage{csquotes}
 \usepackage[author=, status=draft]{fixme}
\usepackage{isomath} %SKB: Changed from \input{isomath} to \usepackage{isomath}
\newcommand{\skb}[1]{
	\begin{quotation}
		\color{Blue} SKB: #1	
	\end{quotation}

}
\newcommand{\debug}[1]{\marginpar{\small\raggedright\begin{spacing}{1}
      \color{BrickRed} #1
\end{spacing}
}}
\newenvironment{response}
{\slshape}{}

\begin{document}
	\section*{General remarks} % which are too long for the margin... .
\begin{itemize}
	\item A rather general remark, I added the occupation variable to the estimations, but did not redo the graphs or tables. The results should not differ much. It will show up in the tables with all coefficients.
\item SKB: The column separating lines in Table 4 have some \enquote{holes}. We might have to switch from the dcolumn package to the siunitx package to fix these issues. I did not manage yet fix these issues. The referees did not complain, but it still looks ugly or strange. 
\end{itemize}
\section*{Response to the referees}

@@

  \begin{response}
    No response needed here.
  \end{response}
\item 
  \debug{OT: should refer to Toomet (2011), maybe there are more
    papers.  The effect is mainly coming from Tallinn and somewhat
    from education too, either do a table that disentangles these, or
    a plot (violin plot?) by group.}
  \debug{SKB: I did the estimation separated by regions, but not 
  separated by regions and educational level. We could add the regional
  breakdown in the appendix or add it as another extension to chapter 6.}
  My main concern is with some of their wage results. I find it
  puzzling that they don’t find a wage premium for Russian men who
  have Estonian language skills as they do find a sizeable significant
  effect of about 11 to 17 percent for Russian women and a significant
  positive effect for Estonians who speak Russian. Furthermore, they
  find that Estonian language skills do reduce the probability of
  being unemployed for Russians. Why is there a reduction in the
  probability of being unemployed, but no wage effect? Can we trust
  this result? Looking at the descriptive statistics (see Table 1) the
  wage for Russian men who speak Estonian seems to be higher compared
  to Russian men without the ability to speak Estonian (489.96 vs
  401.59). The authors should either provide more statistics on this
  result (if possible) or a more detailed discussion on potential
  reasons that lead to this finding.
\item
  \debug{OT: I'll do a rewrite after changes are made, hope it's
    sufficient.} 
  The paper needs to be checked for spelling and grammar
  errors. There are a number of typos and errors, which should be
  corrected in a revision. This would normally be a minor comment, but
  here the authors should take this comment very serious as there are
  so many mistakes.
\end{enumerate}

\subsection{Minor comments:}

\begin{enumerate}
\item- The description of the estimation models in Chapter 4 should
  be more detailed. Please describe more specifically what exactly you
  are estimating. In particular the description of the second model
  estimating the time trend is very short.
  \debug{SKB: Svetlana modified the equations a bit. I added another table,
  which summarises the models.}
\item - The tables and figures should have notes that explain in more
  detail what is shown in the respective table and figure. For
  instance, the table notes should contain the included control
  variables, the sample period and the age restriction applied.
  \debug{SKB: I added this information to the tables and the figures. The descriptions might need some polishing still.}
\item 
- Page 4: You write that you are only analysing individuals who are
working or actively looking for a job, but in line 35 on the same page
you write that inactivity is one of the included labour market
outcomes. Please clarify this and be clear in your description of what
is included in your sample.
\item 
  \debug{ot: let's make it equal (i.e. remove all observations with
    any of the variables missing.  Add a footnote that when we
    included all the variables, we still got the same results.}
\debug{SKB: I estimated the models, but did not create yet the tables.}
  The sample size for different specification of the same analysis
should be the equal. Otherwise it is difficult to conclude whether the
changes in the coefficients are coming from the addition of more
controls or form the change in the size of the estimation sample.
\item 
- In the paper, you are only showing the results of the variables of
interest. I suggest to provide tables including all coefficients (not
the year dummies) in the Appendix. It might be interesting to see how
the coefficients of the control variables change across the different
models.
\debug{SKB: Will add them after I figured out how to present the results nicely formatted. It boils down to finding the right options for the \enquote{estout} or the \enquote{outtex/outreg} user provided package in Stata. I could do the formatting in Excel myself, but I prefer the Stata solution. }
\item 
- All tables: Be consistent in the description of your tables. The
table notes and the labels for e.g., "observations", are inconsistent
across the different tables. 
\debug{SKB: Fixed. Changed obs to observations}
\item
  \debug{ot: this was because of both 'B. Chiswick' and
    'B. R. Chiswick' in the bibtex file, and bibtex wanted to
    distinguish between these two guys.}
 Page 1: To cite Chiswick you are using different versions
(B. Chiswick and B. R. Chiswick).

@@

\begin{response}
  We have corrected the different references.
\end{response}

\item 
- Page 2, line 58: Not the unemployment rate, but the probability of
being unemployed is reduced.
\debug{SKB: Got fixed by Svetlana I think.}
\item 
- Page 3, lines 46-50: You are using a comma as the decimal separator, but in all your tables you are using a point. Please use a point everywhere. 
\debug{SKB: Fixed by someone.}
\end{enumerate}

### 2018-07-03 paper/ijm.tex
Made a couple of minor changes to the text.

 \usepackage[author=, status=draft]{fixme}
\usepackage{longtable}
\usepackage{paralist}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage[natbibapa]{apacite}
%\usepackage[authoryear]{natbib}
\usepackage{csquotes}
%modifying the thanks commands
\usepackage{titling}
\usepackage[colorlinks=true, urlcolor=blue, citecolor=black, linkcolor=black]{hyperref}
\usepackage[noabbrev,capitalise]{cleveref}

@@

\def\tenpc{$^{\ast}$}
\def\fivepc{$^{\ast\ast}$}
\def\onepc{$^{\ast\ast\ast}$}
\newcommand{\legend}{\normalsize{Significance levels:\hspace{1em} \tenpc : 10\% \hspace{1em} \fivepc : 5\% \hspace{1em} \onepc : 1\% \normalsize}}
\def\sep{0.5em}
\def\legendTwo{\multicolumn{3}{l}{\footnotesize{Significance levels
			:\hspace{1em} $\dag$ : 10\% \hspace{1em}
			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
\renewcommand{\thesection}{\arabic{section}.}
\renewcommand{\thesubsection}{\thesection\arabic{subsection}.}

@@

%\fxnote{Add here another index g to denote the group? I used it in other articles, because it was requested and it makes sense}
We estimate the basic model in the following form:
\begin{equation}
	\label{eq:specification}
	\begin{split}
		y_{it} ^{g} = &\: 
		\\alpha^{g}{}' X_{it}^{g}+
		\\& + \vec{beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
		\eta_{i}^{g} +
		\upsilon_{t}^{g} + \epsilon_{it}^{g},
	\end{split}
\end{equation}
where $y_{it}^{g}$ is the outcome (either unemployment indicator
or logarithm of net monthly wage)
of individual $i$ in wave $t$ from ethnic group g; $\vec{X}^{g}$ are the other individual
characteristics for both groups; $L$ is the vector of
language skill descriptors, $eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}^{g}$ are the year dummies and $\epsilon_{it}^{g}$
is the idiosyncratic error term. We denote the groups g by E (Estonian) and R (Russian).
As we use panel data, we cluster the
standard errors on individuals.  When analysing the time trend, we
replace the main language effects in~\eqref{eq:specification} by the
\fxnote*{Did we estimate it really that way? At least not in my code.}{corresponding interactions}
\begin{align}
	\label{eq:time_interaction}
	\beta_{RUS,t} \cdot RUS_{it} \cdot \upsilon_{t} +
	\beta_{EST,t} \cdot EST_{it} \cdot \upsilon_{t} +
	\beta_{ENG,t} \cdot ENG_{it} \cdot \upsilon_{t}.
\end{align}

We estimate three models that differ in terms of the number of
control variables. The first one only includes the language skills
and year dummies. The second one also includes individual
characteristics (age, education) and family descriptors (marital status, having kids up to 17 years old) and county of residence.
Finally, the third model additionally includes industry, occupation, and other
workplace descriptors.

@@

\begin{table}[t!]
	\begin{center}
		\caption{Estimation results for unemployment.}
		\label{tab:unemployment_estimation_by_sex_and_ethnic}
		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&         \multicolumn{2}{c}{Men}         &        \multicolumn{2}{c}{Women}        \\
			Estonians:      & \multicolumn{1}{c}{1}      & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      \\
			Russian         & -0.026^{***}               & -0.010                             & -0.009^{*}                 & 0.010^{**}                 \\
			                & (0.006)                    & (0.006)                            & (0.005)                    & (0.005)                    \\
			English         & -0.047^{***}               & -0.019^{***}                       & -0.024^{***}               & -0.008^{*}                 \\
			                & (0.004)                    & (0.005)                            & (0.004)                    & (0.004)                    \\
			\# obs          & \multicolumn{1}{c}{36,160} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,050} & \multicolumn{1}{c}{36,015} \\
			$R^{2}$         & 0.022                      & 0.047                              & 0.012                      & 0.036                      \\ \hline
			Russians: & \\
			Estonian        & -0.052^{***}               & -0.052^{***}                       & -0.065^{***}               & -0.045^{***}               \\
			                & (0.010)                    & (0.011)                            & (0.009)                    & (0.010)                    \\
			English         & -0.020                     & 0.006                              & -0.015                     & -0.003                     \\
			                & (0.012)                    & (0.014)                            & (0.011)                    & (0.012)                    \\
			\# obs          & \multicolumn{1}{c}{12,946} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,689} & \multicolumn{1}{c}{13,674} \\
			$R^{2}$         & 0.033                      & 0.066                              & 0.023                      & 0.043                      \\ \hline
			year dummies    & \V                         & \V                                 & \V                         & \V                         \\
			indiv. charact. &                            & \V                                 &                            & \V                         \\
			\bottomrule
		\end{tabular}%
		\begin{flushleft}
			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.}
		\end{flushleft}
	\end{center}

@@

			\# obs             & \multicolumn{1}{l}{22,290} & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{22,274}         & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,449} & \multicolumn{1}{c}{26,644} \\

@@

			\# obs             & \multicolumn{1}{l}{8234}   & \multicolumn{1}{l}{7978}   & \multicolumn{1}{l}{8233}           & \multicolumn{1}{l}{9904}   & \multicolumn{1}{l}{9697}   & \multicolumn{1}{c}{9895}   \\

@@

			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis}

@@

		\label{fig:long-run_unemployment_estonian_russian_men}
	}
	\subfigure[Non-native languages for women]{
		\includegraphics[width=0.45\linewidth]{Figure1b.eps}
		\label{fig:long-run_unemployment_estonian_russian_women}
	}
	\subfigure[English for Men]{
		\includegraphics[width=0.45\linewidth]{Figure1c.eps}
		\label{fig:long-run_unemployment_english_men}
	}
	\subfigure[English for Women]{
		\includegraphics[width=0.45\linewidth]{Figure1d.eps}
		\label{fig:long-run_unemployment_english_women}
	}
	\caption{The effect of language fluency on unemployment, 1992--2012}
	\label{fig:long-run_unemployment}
\end{figure}

@@

\begin{figure}[hbtp]
	\centering
	\subfigure[Non-native languages for men]{
		\includegraphics[width=0.45\linewidth]{Figure2a.eps}
		\label{fig:long-run_wage_estonian_russian_men}
	}
	\subfigure[Non-native languages for women]{
		\includegraphics[width=0.45\linewidth]{Figure2b.eps}
		\label{fig:long-run_wage_estonian_russian_women}
	}
	\subfigure[English for Men]{
		\includegraphics[width=0.45\linewidth]{Figure2c.eps}
		\label{fig:long-run_wage_english_men}
	}
	\subfigure[English for Women]{
		\includegraphics[width=0.45\linewidth]{Figure2d.eps}
		\label{fig:long-run_wage_english_women}
	}
	\caption{The effect of language fluency on wage, 1992--2012}
	\label{fig:long-run_wage}
\end{figure}

@@

\begin{table}[t]
	\centering
	\caption{Language environment and language need at workplace:
		regression results}
	\label{tab:environment_model}
	\begin{tabular}{l r@{}l r@{}l r@{}l}
		\toprule
		Dependent variable: & \multicolumn{2}{c}{Need Estonian} & \multicolumn{2}{c}{Use Estonian} & \multicolumn{2}{c}{Need English} \\ \midrule
		woman             & 0.262       & **  & 0.162       & *   & -0.045      &   \\
		                  & \std{0.117} &     & \std{0.095} &     & \std{0.192} &   \\
		college education & 0.201       & **  & 0.132       & **  & 0.133       & * \\
		                  & \std{0.083} &     & \std{0.067} &     & \std{0.079} &   \\
		region Tallinn    & -0.276      & *** & -0.463      & *** & 0.036       &   \\
		                  & \std{0.083} &     & \std{0.067} &     & \std{0.080} &   \\
		region North-East & -0.527      & *** & -0.473      & *** & 0.022       &   \\
		                  & \std{0.091} &     & \std{0.074} &     & \std{0.088} &   \\ \midrule
		N obs             & 228         &     & 228         &     & 228         &   \\
		$R^{2}$           & 0.2598      &     & 0.2831      &     & 0.108       &   \\ \bottomrule
	\end{tabular}
	\begin{flushleft}
		Note: control variables include: marital status, education,
		occupation and age.
	\end{flushleft}
\end{table}

@@

>>>>

 \usepackage[author=, status=final]{fixme}
  \usepackage[final]{changes} %Manually track changes
 \definechangesauthor{SKB}
\usepackage{longtable}
\usepackage{paralist}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage[natbibapa]{apacite}
%\usepackage[authoryear]{natbib}
\usepackage{csquotes}
%modifying the thanks commands
\usepackage{titling}
\usepackage[colorlinks=true, urlcolor=blue, citecolor=black, linkcolor=black]{hyperref}
\usepackage[noabbrev,capitalise]{cleveref}

@@

\def\tenpc{$^{\ast}$}
\def\fivepc{$^{\ast\ast}$}
\def\onepc{$^{\ast\ast\ast}$}
\newcommand{\legend}{\normalsize{Significance levels:\hspace{1em} \tenpc : 10\% \hspace{1em} \fivepc : 5\% \hspace{1em} \onepc : 1\% \normalsize}}
\def\sep{0.5em}
\def\legendTwo{\multicolumn{3}{l}{\footnotesize{Significance levels
			:\hspace{1em} $\dag$ : 10\% \hspace{1em}
			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
%SKB: Added for documenting the tables and figures
\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, being married, number of children, inter-ethnic household}
\newcommand{\modelThree}{\modelTwo, industry, occupation ,ownership type of company, number of workers in company, working in the public sector, experience in company}
\newcommand{\modelThreeAdd}{industry, occupation ,ownership type of company, number of workers in company, working in the public sector, experience in company}	
\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons
	25-55 year old.}
\newcommand{\agerestrictions}{Sample is limited to persons
	25-55 year old.}
%Modified section numbering	
\renewcommand{\thesection}{\arabic{section}.}
\renewcommand{\thesubsection}{\thesection\arabic{subsection}.}

@@

%\fxnote{Add here another index g to denote the group? I used it in other articles, because it was requested and it makes sense}
We estimate the basic model in the following form:
\begin{equation}
	\label{eq:specification}
	\begin{split}
		y_{it} ^{g} = &\: alpha^{g}{}' X_{it}^{g} + \vec{beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
		\eta_{i}^{g} +
		\upsilon_{t}^{g} + \epsilon_{it}^{g},
	\end{split}
\end{equation}
where $y_{it}^{g}$ is the outcome (either unemployment indicator
or logarithm of net monthly wage)
of individual $i$ in wave $t$ from ethnic group g; $\vec{X}^{g}$ are the other individual
characteristics for both groups; $L$ is the vector of
language skill descriptors, $eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}^{g}$ are the year dummies and $\epsilon_{it}^{g}$
is the idiosyncratic error term. We denote the groups g by E (Estonian) and R (Russian).
As we use panel data, we cluster the
standard errors on individuals.  When analysing the time trend, we
replace the main language effects in~\eqref{eq:specification} by the
\fxnote*{Did we estimate it really that way? At least not in my code. I found the code for estimations with these interactions, but I don't remember that I used these interactions for the tables.}{corresponding interactions}
\begin{align}
	\label{eq:time_interaction}
	\beta_{RUS,t} \cdot RUS_{it} \cdot \upsilon_{t} +
	\beta_{EST,t} \cdot EST_{it} \cdot \upsilon_{t} +
	\beta_{ENG,t} \cdot ENG_{it} \cdot \upsilon_{t}.
\end{align}

We estimate three models that differ in terms of the number of
control variables. The first one only includes the language skills
and year dummies. The second one also includes individual
characteristics (age, education) and family descriptors (marital status, having kids up to 17 years old) and county of residence.
Finally, the third model additionally includes industry, occupation, and other
workplace descriptors.
\Cref{tab:models} summarises this description of the models.
%SKB: This table should have been in the article at some point, but I must have removed it. I use in my Quantile Regression article
\begin{table}[hbtp]
	\centering
	\caption{Groups of explanatory variables included in different models}
	\label{tab:models}
	\begin{tabular}{r|ccc}
		\toprule
		& Model 1 & Model 2 & Model 3 \\ \midrule
		year dummies       & \V      & \V      & \V      \\
		indiv. charact.    &         & \V      & \V      \\
		workplace charact. &         &         & \V      \\ 
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{table}[t!]
	\begin{center}
		\caption{Estimation results for unemployment.}
		\label{tab:unemployment_estimation_by_sex_and_ethnic}
		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&         \multicolumn{2}{c}{Men}         &        \multicolumn{2}{c}{Women}        \\
			Estonians:      & \multicolumn{1}{c}{1}      & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      \\
			Russian         & -0.026^{***}               & -0.010                             & -0.009^{*}                 & 0.010^{**}                 \\
			                & (0.006)                    & (0.006)                            & (0.005)                    & (0.005)                    \\
			English         & -0.047^{***}               & -0.019^{***}                       & -0.024^{***}               & -0.008^{*}                 \\
			                & (0.004)                    & (0.005)                            & (0.004)                    & (0.004)                    \\
			\# observations          & \multicolumn{1}{c}{36,160} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,050} & \multicolumn{1}{c}{36,015} \\
			$R^{2}$         & 0.022                      & 0.047                              & 0.012                      & 0.036                      \\ \hline
			Russians: & \\
			Estonian        & -0.052^{***}               & -0.052^{***}                       & -0.065^{***}               & -0.045^{***}               \\
			                & (0.010)                    & (0.011)                            & (0.009)                    & (0.010)                    \\
			English         & -0.020                     & 0.006                              & -0.015                     & -0.003                     \\
			                & (0.012)                    & (0.014)                            & (0.011)                    & (0.012)                    \\
			\# observations          & \multicolumn{1}{c}{12,946} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,689} & \multicolumn{1}{c}{13,674} \\
			$R^{2}$         & 0.033                      & 0.066                              & 0.023                      & 0.043                      \\ \hline
			year dummies    & \V                         & \V                                 & \V                         & \V                         \\
			indiv. charact. &                            & \V                                 &                            & \V                         \\
			\bottomrule
		\end{tabular}%
		\begin{flushleft}
			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.\\  Individual characteristics are \modelTwo. \\ \restrictions}
		\end{flushleft}
	\end{center}

@@

			\# observations             & \multicolumn{1}{l}{22,290} & \multicolumn{1}{l}{22,274} & \multicolumn{1}{l}{21,785}         & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,644} & \multicolumn{1}{c}{26,449} \\

@@

			\# observations             & \multicolumn{1}{l}{8234}   & \multicolumn{1}{l}{8233}   & \multicolumn{1}{l}{7978}           & \multicolumn{1}{l}{9904}   & \multicolumn{1}{l}{9895}   & \multicolumn{1}{c}{9697}   \\

@@

			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis \\ Individual characteristics are \modelTwo. \\ Workplace characteristics are \modelThreeAdd. \\ \restrictions}

@@

		\label{fig:long-run_unemployment_estonian_russian_men}
	}
	\subfigure[Non-native languages for women]{
		\includegraphics[width=0.45\linewidth]{Figure1b.eps}
		\label{fig:long-run_unemployment_estonian_russian_women}
	}
	\subfigure[English for Men]{
		\includegraphics[width=0.45\linewidth]{Figure1c.eps}
		\label{fig:long-run_unemployment_english_men}
	}
	\subfigure[English for Women]{
		\includegraphics[width=0.45\linewidth]{Figure1d.eps}
		\label{fig:long-run_unemployment_english_women}
	}
	\caption{The effect of language fluency on unemployment, 1992--2012. \\ Control variables are \modelTwo. \agerestrictions }
	\label{fig:long-run_unemployment}
\end{figure}

@@

\begin{figure}[hbtp]
	\centering
	\subfigure[Non-native languages for men]{
		\includegraphics[width=0.45\linewidth]{Figure2a.eps}
		\label{fig:long-run_wage_estonian_russian_men}
	}
	\subfigure[Non-native languages for women]{
		\includegraphics[width=0.45\linewidth]{Figure2b.eps}
		\label{fig:long-run_wage_estonian_russian_women}
	}
	\subfigure[English for Men]{
		\includegraphics[width=0.45\linewidth]{Figure2c.eps}
		\label{fig:long-run_wage_english_men}
	}
	\subfigure[English for Women]{
		\includegraphics[width=0.45\linewidth]{Figure2d.eps}
		\label{fig:long-run_wage_english_women}
	}
	\caption{The effect of language fluency on wage, 1992--2012. \\ Control variables are \modelTwo. \agerestrictions}
	\label{fig:long-run_wage}
\end{figure}

@@

\begin{table}[t]
	\centering
	\caption{Language environment and language need at workplace:
		regression results}
	\label{tab:environment_model}
	\begin{tabular}{l r@{}l r@{}l r@{}l}
		\toprule
		Dependent variable: & \multicolumn{2}{c}{Need Estonian} & \multicolumn{2}{c}{Use Estonian} & \multicolumn{2}{c}{Need English} \\ \midrule
		woman             & 0.262       & **  & 0.162       & *   & -0.045      &   \\
		                  & \std{0.117} &     & \std{0.095} &     & \std{0.192} &   \\
		college education & 0.201       & **  & 0.132       & **  & 0.133       & * \\
		                  & \std{0.083} &     & \std{0.067} &     & \std{0.079} &   \\
		region Tallinn    & -0.276      & *** & -0.463      & *** & 0.036       &   \\
		                  & \std{0.083} &     & \std{0.067} &     & \std{0.080} &   \\
		region North-East & -0.527      & *** & -0.473      & *** & 0.022       &   \\
		                  & \std{0.091} &     & \std{0.074} &     & \std{0.088} &   \\ \midrule
		\# observations             & 228         &     & 228         &     & 228         &   \\
		$R^{2}$           & 0.2598      &     & 0.2831      &     & 0.108       &   \\ \bottomrule
	\end{tabular}
	\begin{flushleft}
		Note: control variables include: marital status, education,
		occupation and age.
	\end{flushleft}
\end{table}

@@

\appendix
\input{appendix.tex}
